Correcting K-correction: dark energy is based on a math error from 1930

### 2025-02-03 paper/dark_energy_corrections.tex

\documentclass[aps,prl,reprint,amsmath]{revtex4-2}

\usepackage{graphicx}

@@

\begin{abstract}
We rederive the K-correction equation and discover that the version commonly
used to calculate magnitudes contains multiple errors. The oldest of these
errors traces back to 1930 and two new errors were introduced in 1996. We
conclude that properly correcting apparent magnitudes for redshift resolves two
of the preeminent mysteries in cosmology: first, dark energy is not supported
by observations of Type Ia supernovae and second, the Hubble tension is due to
the errors in the K-correction equation.
\end{abstract}

@@

The estimate of Type Ia supernovae (SnIa) distances is one of the primary
sources of data for cosmological models. Performing these distance estimates
involves taking a measurement of redshifted light in our observation frame and
then calculating the rest frame magnitude as if no redshift had occurred. The
equation that converts from an observation frame magnitude to a rest frame
magnitude is called K-correction.

\citet{tolman1930} published the first formal derivation of K-correction, but
he did not account for spectral bandwidth stretching, one of the dimming
effects of redshift. An alternative K-correction was correctly derived by
\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy was
briefly discussed yet dismissed. \citet{oke1968} rederived the K-correction
equation where they accounted for spectral bandwidth stretching, but they did
not account for time dilation, one of the other dimming effects of redshift.
The paper by \citet{kim1996}, which is the basis for modern implementations of
K-correction, extended the work of \citet{oke1968} to handle additional
cross-filter comparisons and added a term that was intended to address
zero-point corrections. This history is explored in more depth in Section
\ref{sec:history}.

The effect of using an incorrect redshift correction for SnIa is that we think
objects are farther away than they really are; this effect compounds for
greater distances. Up until \citet{riess1998}, we did not have distant enough
observations for this error to matter much for cosmological models, but by the
late 1990s, it became clear that our measurements for distance and redshift
were not linear. This realization led to a model that utilized a cosmological
constant $\Lambda$ and dark energy in order to explain the non-linear
distance-redshift graph. We will show in Section \ref{sec:conclusions} that
correcting the flaws of K-correction leads to a linear graph that does not
need to rely on a cosmological constant.

\citet{planck2015} used an alternative technique to compute the Hubble constant
$H_0$ that is based on measurements of the cosmic microwave background (CMB).
CMB-based computations of $H_0$ have made it evident that something is missing
with our understanding of cosmology because this technique produces a
significantly different value than when the constant is derived using SnIa.  As
we will discuss in Section \ref{sec:conclusions}, fixing the errors with
K-correction produces a measurement of the Hubble constant that is compatible
with models based on the CMB.

\section{A brief history of K-correction}
\label{sec:history}

Observational data from SnIa are essential for the calibration of models that
use redshift to estimate distance. The approximately linear relationship
between redshift and luminosity distance, often called the Hubble-Lema\^{i}tre law,
describes how quickly the universe is expanding. However, \citet{riess1998}
and \citet{perlmutter1999} presented evidence that there is not a linear
relationship between redshift and distance, but instead, distant objects are
farther away than their redshift would predict (see Figure
\ref{fig:mu_distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
The cause of this phenomenon was unknown and was referred to as dark energy.

\begin{figure}
  \includegraphics[width=\columnwidth]{lum_distance_vs_redshift.pdf}
  \caption{The relationship between luminosity distance and redshift for two
  treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
  the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
  treatment, which fixes the K-correction redshift error, appears to be linear.
  The displayed points are roughly a third of the values in the full SnIa
  dataset published in \citet{abbott2024}, selected with uniform redshift
  spacing to aid visibility. }
  \label{fig:mu_distance_vs_redshift}
\end{figure}

SnIa are used to explore the relationship between distance and redshift because
these events have a roughly constant absolute magnitude, which allows us to use
the apparent magnitude to estimate distance. An analogy is to imagine someone
walking in the dark and lighting matches. If we know how brightly a match burns
at a known distance, we can estimate the distance to any match by measuring the
apparent brightness before applying some geometry.

However, redshifting dims the luminosity of an observation in three ways:

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength; thus a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of $1 / (1+z)$.

  \item The bandwidth stretches. If the rest frame observes photons in the
  bandwidth from 400nm and 401nm, then a redshift of $z = 1$ stretches the
  wavelengths to the bandwidth from 800nm to 802nm. The number of photons per
  bandwidth is reduced by a factor of $1 / (1+z)$.

  \item Cosmological time dilation reduces the rate at which photons arrive.
  The number of photons that arive per second is reduced by a factor of $1 / (1+z)$.
\end{itemize}

To complicate matters, we use the $B$ band magnitude to calculate luminosity
distance. We want to know how bright a supernova appears for wavelengths around
445nm as if no redshift had occurred. However, we typically need to observe the
supernova with a filter that is sensitive to longer wavelengths, such as the
$i$ band filter which is sensitive to wavelengths from 700nm-850nm
\citep{flaugher2015}. The K-correction formula allows us to take a magnitude
measured in an observation filter $y$ and compute the magnitude in the target
filter $x$.

@@

A few years later, \citet{desitter1934} discussed all three issues that reduce
the observed magnitude of a distant observation. The correction for each of
these issues is identical: take a measurement for luminosity and multiply it by
the factor $1 + z$.

A year later, \citet{hubble1935} published a similar set of calculations where they noted:

@@

In a paper published by \citet{oke1968}, the two factors of $(1 + z)$ were
attributed to the change in energy and to the spectral bandwidth elongation,
which leaves time dilation as the factor that was omitted.

The modern treatment of K-correction is based on the work of \citet{kim1996}.
This work extended the work of \citet{oke1968} to apply to filters beyond the
blue $B$ and visible $V$ bands. It also introduced a term that deals with the
zero-point for the actual filters. Historically, bolometric devices would
measure the energy flux, but modern charge-coupled device (CCD) cameras
effectively measure the photon flux, so \citet{kim1996} derived a form of the
K-correction equation that uses photon flux.

Quoting \citet{kim1996}:

\begin{quote}
  Therefore, the correct K correction calculation to be used with measured
  photometric magnitudes is the integral photon counts:

  \begin{equation}
  \begin{aligned}
  \label{eq:kim}
    K_{xy} =
      &-2.5\text{log} \left(
        \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
             {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) \\
      &+ 2.5\text{log}(1+z) \\
      &+ 2.5\text{log}\left(
        \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
             {\int \lambda F(\lambda/(1+z))S_y(\lambda))d\lambda}\right).
  \end{aligned}
  \end{equation}
\end{quote}

This equation has three errors that we will explore in Section
\ref{sec:consequences}.

\section{Derivation of K-correction}
\label{sec:derivation}

The K-correction $K_{xy}$ uses a spectral energy density $F$ template that
specifies the expected spectrum for a SnIa observation. It also uses the
observed redshift $z$ and the observed photon flux magnitude $m_y$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
  report in the target filter divided by the number of photons we measure in
  the observation filter. Deriving this value starts with $F(\lambda)$, the
  spectral energy density, which we then convert to $F'(\lambda)$, the photon
  density for the rest frame. Starting at the top right corner of the figure we
  show three steps used to compute $R'(\lambda)$, the photon density in the
  observation frame. We first stretch the photon density, but this step
  inflates counts. In the second step, we correct for the inflated counts by
  multiplying by $1/(1+z)$; at this point, the total count equals the total
  count of $F'(\lambda)$. Finally, in the third step we finish calculating the
  observation frame photon density $R'(\lambda)$ by accounting for time
  dilation, which also reduces photon counts by a factor of $1/(1+z)$. We can
  compute the expected ratio of photons by totalling the area under the curves
  in the bottom two panels.
  }
  \label{fig:k-example}
\end{figure}

@@

\begin{equation}
\begin{aligned}
\label{eq:as_flux}
  -2.5 \text{log}(\mathcal{F}_x)
      &= m_x - P_x \\
      &= m_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y) \\
         &\qquad - 2.5 \text{log}(P'_y) \\
         &\qquad - 2.5 \text{log}(K'_{xy}) \\
         &\qquad + 2.5 \text{log}(P'_x) \\
      &= -2.5 \biggl(\text{log}(\mathcal{F}_y) + \text{log}(K'_{xy}) \\
         &\qquad\qquad + \text{log}(P'_y) - \text{log}(P'_x)
        \biggr) \\
      &= -2.5 \text{log}\left(
        \mathcal{F}_y
        \times K'_{xy}
        \times \frac{P'_y}{P'_x}\right) \\
  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x}.
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int R'(\lambda) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int F'\left(\frac{\lambda}{1+z}\right) \times \left(\frac{1}{1 + z}\right)^2 S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
              \frac{\int \left(\frac{\lambda}{hc}\right) F(\lambda) S_x(\lambda) d\lambda}
                   {\int \left(\frac{\lambda}{(1+z)hc}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
         &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\label{eq:K2k}
  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
         &= 2.5\text{log}\left(
            \frac{P'_x}{P'_y} \times (1 + z)^2 \times
            \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                 {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda}\right) \\
         &= 2.5 \left(
            \text{log} \left( \frac{P'_x}{P'_y} \right)
            + \text{log}( {(1 + z)^2})
            + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                                    {\int (\lambda / (1+z)) F((\lambda)/ (1+z)) S_y(\lambda) d\lambda}
            \right) \right) \\
         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
            - P_x + P_y .
\end{aligned}
\end{equation}

\section{Consequences}
\label{sec:consequences}

In order to fully compare our derivation against Equation \ref{eq:kim} (from
\citet{kim1996}) we need to use the identity

@@

\begin{equation}
\begin{aligned}
  K_{xy} &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right)
            - P_x + P_y \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) \\ &\ \ \
            + 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right)
            - 2.5 \text{log} \left( \int (\lambda / hc) \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
         &= 2.5 \text{log} \left(
              \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
                   {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
             \right)
            + 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int (\lambda / (1+z)) F(\lambda / (1+z)) S_y(\lambda) d\lambda} \right) .
\end{aligned}
\end{equation}

@@

\section{Conclusions}
\label{sec:conclusions}

\begin{figure}
  \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and distance. The slope
  of this graph demonstrates the Hubble constant. The data for these SnIa
  observations comes from the Dark Energy Survey \citep{vincenzi2024}, but the
  magnitudes are corrected to account for time dilation by adding
  $-2.5 log(1 + z)$.
  }
\label{fig:expansion}
\end{figure}

As shown in Figure \ref{fig:mu_distance_vs_redshift}, when reported magnitudes
are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
relationship between redshift and luminosity distance. This is in accordance
with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
is no visual acceleration. Since the corrected values are approximately linear,
we can use them to estimate the Hubble constant $H_0$ which is demonstrated in
Figure \ref{fig:expansion}.

The value estimated here, $H_0 = 65.94 \pm 1.3$ is highly suspicious
because of the flipped zero-point corrections, but it is consistent with
estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap. It
is interesting to note that restricting the Dark Energy Survey observations of
SnIa \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
small enough redshift that most of the observations will have been made with
the same filter, gives the estimate $H_0 = 67.8 \pm 1.9$.

@@

\bibliography{references}{}
\bibliographystyle{aasjournal}

>>>>

\documentclass[aps,prl,reprint,amsmath,floatfix]{revtex4-2}

\usepackage{graphicx}
\usepackage{relsize}

@@

\begin{abstract}
We rederive the K-correction equation and discover that the version commonly
used to calculate magnitudes contains multiple errors. The oldest of these
errors traces back to 1930 and two new errors were introduced in 1996. We
conclude that correcting apparent magnitudes for time dilation resolves two of
the preeminent mysteries in cosmology: first, dark energy is not supported by
observations of Type Ia supernovae and second, the Hubble tension is due to the
errors in the K-correction equation.
\end{abstract}

@@

Cosmic expansion redshifts light, so when we compute the light travel distance
it is necessary to account for multiple redshift effects. We will show that
modern cosmology does not correct observations for time dilation.

Most cosmological models require an estimate of distance, so this error is far
reaching. However, we will focus on showing that correcting observations of
Type Ia supernovae (SNe Ia) for time dilation resolves the Hubble tension. The
Hubble tension, as described by \citet{verde2019}, is an observation that
independent techniques of estimating the expansion rate produce incompatible
values.

In order to use SNe Ia to estimate the expansion rate of the universe, we need to
identify both the redshift $z$ and the light travel distance $d$. In order to
compute the light travel distance $d$, we use the definition of the distance
modulus \citep{weinberg2008}:

\begin{equation}
\label{eq:mu_def}
  d = 10^{1 + (m - M)/5} \text{pc}.
\end{equation}

\noindent The quantity $m$ represents the apparent magnitude while $M$
represents the absolute magnitude of a SN Ia. It is common to use the
substitution $\mu = m - M$ and call $\mu$ the distance modulus.

Labeling $m$ as the ``apparent magnitude'' is a bit misleading for distant
observations because redshift will change several aspects of the observed
light. However, we can correct the value $m$ for redshift effects by using the
K-correction equation. This allows us to report an apparent magnitude that
represents the brightness of an object as if none of the light-altering effects
of redshift were present. According to
\citet{riess1998}:

\begin{quote}
  An appropriate K-correction quantifies the difference between the supernova
  light that falls into a standard passband (e.g., $B$) at $z_0$ and that which
  falls into the filters we employ to observe a redshifted SN Ia.
\end{quote}

\noindent In other words, the goal of the K-correction equation is to remove
all redshift effects from the apparent magnitude $m$ so that the distance
modulus defined in Equation \ref{eq:mu_def} allows us to compute the light
travel distance $d$.

\citet{tolman1930} published the first formal derivation of K-correction, but
he did not account for spectral bandwidth stretching, one of the dimming
effects of redshift. An alternative K-correction was correctly derived by
\citet{desitter1934}. However, in \citet{hubble1935}, the discrepancy between
the two equations was briefly discussed yet ultimately dismissed.
\citet{oke1968} derived a K-correction equation that they noted was equivalent
to earlier work, and while they accounted for spectral bandwidth stretching,
they did not account for time dilation. The paper by \citet{kim1996}, which is
the basis for modern implementations of K-correction, extended the work of
\citet{oke1968} to handle additional cross-filter comparisons and added a term
that was intended to address zero-point corrections.

The effect of using an incorrect redshift correction for SNe Ia is that we think
objects are farther away than they really are; this effect compounds for
greater distances. Up until \citet{riess1998}, we did not have distant enough
observations for this error to matter much for cosmological models, but by the
late 1990s, it became clear that our measurements for distance and redshift
were not linear. This realization led to a model that utilized a cosmological
constant $\Lambda$ and dark energy in order to explain the non-linear
distance-redshift graph. We will show that correcting the flaws of K-correction
leads to a linear graph that does not need to rely on a cosmological constant.

\citet{planck2015} used an alternative technique to compute the Hubble constant
$H_0$ that is based on measurements of the cosmic microwave background (CMB).
CMB-based computations of $H_0$ have made it evident that something is missing
with our understanding of cosmology because this technique produces a
significantly different value than when the constant is derived using SNe Ia.
Fixing the errors with K-correction produces a measurement of the Hubble
constant that is compatible with models based on the CMB.

\section{A brief history of K-correction}

Observational data from SNe Ia are essential for the calibration of models that
use redshift to estimate distance. The approximately linear relationship
between redshift and light travel distance, often called the
Hubble-Lema\^{i}tre law, describes how quickly the universe is expanding.
However, \citet{riess1998} and \citet{perlmutter1999} presented evidence that
there is not a linear relationship between redshift and distance, but instead,
distant objects are farther away than their redshift would predict (see Figure
\ref{fig:distance_vs_redshift}). This phenomenon implies that the
acceleration of the universe is faster today than it was for old observations.
The cause of this phenomenon was unknown and was referred to as dark energy.

\begin{figure}
  \includegraphics[width=\columnwidth]{distance_vs_redshift.pdf}
  \caption{The relationship between light travel distance and redshift for two
  treatments of the magnitude data. The red $k(z) = 1$ treatment, which represents
  the uncorrected values, is clearly non-linear while the blue $k(z) = 1 + z$
  treatment, which fixes the K-correction redshift error, appears to be linear.
  The displayed points are roughly a third of the values in the full SNe Ia
  dataset published in \citet{abbott2024}, selected with uniform redshift
  spacing to aid visibility. }
  \label{fig:distance_vs_redshift}
\end{figure}

SNe Ia are used to explore the relationship between distance and redshift because
these events have a roughly constant absolute magnitude which allows us to use
the apparent magnitude to estimate distance.

However, redshifting dims the brightness of an observation in three ways:

\begin{itemize}
  \item The energy of a wave is inversely proportional to its wavelength; thus a
  redshift of $z$ means the amount of energy per photon is reduced by a factor
  of ${1 / (1+z)}$.

  \item The bandwidth stretches. If the rest frame observes photons in the
  bandwidth from 400nm and 401nm, then a redshift of ${z = 1}$ stretches the
  wavelengths to the bandwidth from 800nm to 802nm. The number of photons per
  bandwidth is reduced by a factor of ${1 / (1+z)}$.

  \item Cosmological time dilation reduces the rate at which photons arrive.
  The number of photons that arive per second is reduced by a factor of ${1 / (1+z)}$.
\end{itemize}

To complicate matters, we use the $B$ band magnitude to calculate light travel
distance. We want to know how bright a supernova appears for wavelengths around
445nm as if no redshift had occurred. However, we typically need to observe the
supernova with a filter that is sensitive to longer wavelengths, such as the
$i$ band filter which is sensitive to wavelengths from 700nm-850nm
\citep{flaugher2015}. The K-correction formula allows us to take a magnitude
measured in an observation filter $y$ and compute the magnitude in the target
filter $x$. Even if the observation filter is the same as the target filter,
the K-correction equation is necessary to remove redshift effects.

@@

A few years later, \citet{desitter1934} discussed all three issues that reduce
the observed brightness of a distant observation. The correction for each of
these issues is identical: take a flux measurement and multiply it by the
factor $1 + z$.

A year later, \citet{hubble1935} published a similar set of calculations where
they stated:

@@

In a paper published by \citet{oke1968}, the two factors of ${1 + z}$ were
attributed to the change in energy and to the spectral bandwidth elongation,
which leaves time dilation as the factor that was omitted.

The modern treatment of K-correction is based on the work of \citet{kim1996}.
This work extended the work of \citet{oke1968} to apply to filters beyond the
blue $B$ and visible $V$ bands. It also introduced a term that deals with the
zero-point correction for the actual filters. Historically, bolometric devices
would measure the energy flux, but modern charge-coupled device (CCD) cameras
effectively measure the photon flux, so \citet{kim1996} derived a form of the
K-correction equation that uses photon flux. This is the form of the
K-correction equation that is used by modern astrophysics, but we will show
that it contains three errors, one of which is innocuous, one of which
introduces measurement bias, and one that produces the dark energy phenomenon.

\section{Derivation of K-correction}

The K-correction $K_{xy}$ uses a spectral energy density template $F$ that
specifies the expected spectrum for a SN Ia observation. It also uses the
observed redshift $z$ and the observed photon flux magnitude $m_y$ measured in
filter $y$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{k_equation_flow.pdf}
  \caption{The value $K'_{xy}$ is equal to the number of photons we want to
  report in the target filter divided by the number of photons we measure in
  the observation filter. Deriving this value starts with $F(\lambda)$, the
  spectral energy density, which we then convert to $F'(\lambda)$, the photon
  density for the rest frame. Starting at the top right corner of the figure we
  show three steps used to compute $R'(\lambda)$, the photon density in the
  observation frame. We first stretch the photon density, but this step
  inflates counts. In the second step, we correct for the inflated counts by
  multiplying by $1/(1+z)$; at this point, the total count equals the total
  count of $F'(\lambda)$. Finally, in the third step we finish calculating the
  observation frame photon density $R'(\lambda)$ by accounting for time
  dilation, which also reduces photon counts by a factor of $1/(1+z)$. We can
  compute the expected ratio of photons by totalling the area under the curves
  in the bottom two panels. Dark energy occurs when we omit the step that
  corrects for time dilation.
  }
  \label{fig:k-example}
\end{figure}

@@

\begin{equation}
\begin{aligned}
\label{eq:as_flux}
  -2.5 \text{log}(\mathcal{F}_x)
      &= m_x - P_x \\
      &= m_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y) + P_y - K_{xy} - P_x \\
      &= -2.5 \text{log}(\mathcal{F}_y) - 2.5 \text{log}(P'_y) \\
         &\qquad - 2.5 \text{log}(K'_{xy}) + 2.5 \text{log}(P'_x) \\
      &= -2.5 \left(\text{log}(\mathcal{F}_y) + \text{log}(K'_{xy}) \right. \\
         &\qquad\qquad + \left. \text{log}(P'_y) - \text{log}(P'_x)
        \right) \\
      &= -2.5 \text{log}\left(
        \mathcal{F}_y
        \times K'_{xy}
        \times \frac{P'_y}{P'_x}\right) \\
  \mathcal{F}_x &= \mathcal{F}_y \times K'_{xy} \times \frac{P'_y}{P'_x}.
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
  K'_{xy} &= \frac{P'_x}{P'_y} \times \frac{\mathcal{F}_x}{\mathcal{F}_y} \\
          &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int R'(\lambda) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times
              \frac{\int F'(\lambda) S_x(\lambda) d\lambda}
                   {\int F'\left(\frac{\lambda}{1+z}\right) \times \left(\frac{1}{1 + z}\right)^2 S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1+z)^2 \times
              \frac{\int \left(\frac{\lambda}{hc}\right) F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{(1+z)hc} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \\
          &= \frac{P'_x}{P'_y} \times (1 + z)^2 \times
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} .
\end{aligned}
\end{equation}

@@

\begin{equation}
\begin{aligned}
\label{eq:K2k}
  K_{xy} &= 2.5\text{log}(K'_{xy}) \\
         &= 2.5\text{log}
  \begin{aligned}[t]
          &\left( \vphantom{\frac{\int}{\left(\frac{\int}{1}\right)}} \right.
              \frac{P'_x}{P'_y} \times (1 + z)^2 \\
          &\left.\quad \times
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}\right)
  \end{aligned} \\
         &= 2.5
  \begin{aligned}[t]
         &\left( \vphantom{\frac{\int}{\left(\frac{\int}{1}\right)}}
            \text{log} \left( \frac{P'_x}{P'_y} \right)
            + \text{log}\left( {(1 + z)^2}\right) \right. \\
         &\left.\quad + \text{log}\left( \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                                    {\int \left(\frac{\lambda}{1+z}\right) F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda}
            \right) \right)
  \end{aligned} \\
         &= 2.5 \text{log} \left( \frac{P'_x}{P'_y} \right)
            + 5 \text{log} (1 + z) \\
            &\quad + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
         &= 5 \text{log} (1 + z)
            + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
            &\quad - P_x + P_y .
\end{aligned}
\end{equation}

\section{Consequences}

The modern version of the K-correction equation was presented by \citet{kim1996}:

\begin{equation}
\begin{aligned}
\label{eq:kim}
  K_{xy} &=
    -2.5\text{log} \left(
      \frac{\int \lambda \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}
           {\int \lambda \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) \\
    &\quad + 2.5\text{log}(1+z) \\
    &\quad + 2.5\text{log}\left(
      \frac{\int \lambda F(\lambda)S_x(\lambda)d\lambda}
           {\int \lambda F\left(\frac{\lambda}{1+z}\right)S_y(\lambda))d\lambda}\right) \quad \text{(incorrect)}.
\end{aligned}
\end{equation}

In order to fully compare Equation \ref{eq:K2k} against Equation \ref{eq:kim} we need to use the identity

@@

\begin{equation}
\begin{aligned}
  K_{xy} &= 5 \text{log} (1 + z) \\
         &\quad + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
         &\quad - P_x + P_y \\
         &= 5 \text{log} (1 + z) \\
         &\quad + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) \\
         &\quad + 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_x(\lambda) d\lambda \right) \\
         &\quad - 2.5 \text{log} \left( \int \frac{\lambda}{hc} \mathcal{Z}(\lambda) S_y(\lambda) d\lambda \right) \\
         &= 2.5 \text{log} \left(
              \frac{\int \lambda \mathcal{Z}(\lambda) S_x(\lambda) d\lambda}
                   {\int \lambda \mathcal{Z}(\lambda) S_y(\lambda) d\lambda}
             \right) \\
         &\quad + 5 \text{log} (1 + z) \\
         &\quad + 2.5 \text{log} \left(
              \frac{\int \lambda F(\lambda) S_x(\lambda) d\lambda}
                   {\int \frac{\lambda}{1+z} F\left(\frac{\lambda}{1+z}\right) S_y(\lambda) d\lambda} \right) .
\end{aligned}
\end{equation}

@@

\section{Conclusions}

\begin{figure}
  \includegraphics[width=\columnwidth]{velocity_vs_distance.pdf}
  \caption{The relationship between expansion velocity and light travel
  distance. The slope of this graph demonstrates the Hubble constant. The data
  for these SN Ia observations comes from the Dark Energy Survey
  \citep{vincenzi2024}, but the magnitudes are corrected to account for time
  dilation by adding $-2.5 \text{log}(1 + z)$.
  }
\label{fig:expansion}
\end{figure}

As shown in Figure \ref{fig:distance_vs_redshift}, when reported magnitudes
are corrected by adding the magnitude $-2.5\text{log}(1+z)$, there is a linear
relationship between redshift and light travel distance. This is in accordance
with the Hubble-Lema\^{i}tre law. As opposed to the uncorrected values, there
is no visual acceleration. Since the corrected values are approximately linear,
we can use them to estimate the Hubble constant $H_0$ which is demonstrated in
Figure \ref{fig:expansion}.

The value estimated here, $H_0 = 65.94 \pm 1.3$, is highly suspicious
because of the flipped zero-point corrections, but it is consistent with
estimates of $H_0$ that are based on the CMB. \citet{planck2020} published the
CMB value of $H_0 = 67.27 \pm 0.6$, and the one sigma error bars overlap. It
is interesting to note that restricting the Dark Energy Survey observations of
SN Ia \citep{vincenzi2024} to only those with $z < 0.1$, which presumably is a
small enough redshift that most of the observations will have been made with
the same filter, gives the estimate $H_0 = 67.8 \pm 1.9$.

@@

\bibliography{references}
